---
title: "Improve User App Usage"
date: "4/18/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
# install.packages('maps')
library(maps)
# install.packages('ggthemes')
library(ggthemes)
library(here)
```

```{r}
# import data
dat.appuse <- read_csv("Data/app_usage.csv", col_names = TRUE)
dat.demo <- read_csv("Data/demographics.csv", col_names = TRUE)
dat.userex <- read_csv("Data/survey_responses.csv", col_names = TRUE)
glimpse(dat.appuse) #Rows: 3,811
glimpse(dat.demo) #Rows: 3,811
glimpse(dat.userex) #Rows: 2,800
```


```{r}
# check data points for each data set
length(unique(dat.appuse$userid)) #N = 3811
length(unique(dat.demo$userid)) #N = 3811 
length(unique(dat.userex$userid)) #N =  1865

dat.userex %>% 
   group_by(time) %>%
   summarise(n())

dat.userex %>% 
  group_by(userid) %>%
  summarise(time_freq = n())  %>% 
  group_by(time_freq) %>%
  summarise(n())

```

```{r}
#merge datasets
dat.appuse.demo <- dat.appuse %>% left_join(
  dat.demo, by = c("userid" = "userid"))
glimpse(dat.appuse.demo)

```

## Data Exploration

### Missing data 

```{r}
dat.appuse.demo %>% 
  summarise_at(vars(day1:day14),
               funs(usersize=sum(is.na(.)))) %>%
  pivot_longer(cols = day1_usersize:day14_usersize,
             names_to = c("day"),
             values_to = c("usersize")) %>%
  separate(col = "day", c("day","type")) %>%
  separate(col = "day", c("name","day"),"day") %>%
  select(day, usersize) %>%
  mutate(day = as.numeric(day)) %>%
  ggplot(aes(x=day, y=usersize)) +
  geom_line() + 
  labs(title = "Missing data per Day",
       y = "User Size (no-login/missing)",
       x = "Day") + 
  scale_x_continuous(  breaks = c(1:14,1)) +
    theme_classic()
```

```{r}
dat.appuse.demo %>% 
  group_by(metro_area) %>%
  summarise_at(vars(day1:day14),
               funs(usersize=sum(is.na(.))))%>%
  pivot_longer(cols = day1_usersize:day14_usersize,
             names_to = c("day"),
             values_to = c("usersize")) %>%
  separate(col = "day", c("day","type")) %>%
  separate(col = "day", c("name","day"),"day") %>%
  select(metro_area, day, usersize)%>%
  mutate(day = as.numeric(day)) %>%
  ggplot(aes(x=day, y=usersize)) +
  geom_line() + 
  labs(title = "Missing data per Day for each metro area",
       y = "User Size (no-login/missing)",
       x = "Day") +
    theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + 
  facet_wrap(~metro_area)

```

### App Usage Trend overtime
Total App Usage per day (before imputation for missing data; averaged by total number of users)
```{r}
 dat.appuse.demo %>% 
    summarise(user_size = n())

dat.appuse.demo %>% 
  summarise_at(vars(day1:day14),
               funs(#usersize=sum(!is.na(.)), 
                    totalappuse=sum(., na.rm = TRUE))
               )  %>%
  pivot_longer(cols = day1_totalappuse:day14_totalappuse,
               names_to = c("day"),
               values_to = c("totalappuse"))%>%
  separate(col = "day", c("day","type")) %>%
  separate(col = "day", c("name","day"),"day") %>% select(-name,-type) %>% 
  mutate(day = as.numeric(day),
         totalappuse_perusesize = totalappuse/3811) %>% 
  ggplot(aes(x=day, y=totalappuse_perusesize)) +
  geom_line() + 
  labs(title = "Total App Usage per Day Per User",
       y = "Total Usage 
       (Averaged by Total Number of Users)",
       x = "Day") +
  scale_x_continuous(  breaks = c(1:14,1)) +
    theme_classic()
```
Total App Usage per day over time (before imputation for missing data; averaged by total available data points per day)
```{r}
# https://uc-r.github.io/ts_exploration
# library(forecast)
# library(fpp2)
dat.appuse.demo %>% 
  summarise_at(vars(day1:day14),
               funs(usersize=sum(!is.na(.)), 
                    totalappuse=sum(., na.rm = TRUE))) %>%
  pivot_longer(cols = day1_usersize:day14_totalappuse,
               names_to = c("day_n_appuse"),
               values_to = c("usersize_totalappuse")) %>%
  separate(col = "day_n_appuse", c("day","type")) %>%
  pivot_wider(
             names_from = c("type"),
             values_from = c("usersize_totalappuse")) %>%
  separate(col = "day", c("name","day"),"day") %>% select(-name) %>% 
  mutate(day = as.numeric(day),
         totaldailyappuse_avg=totalappuse/usersize) %>%
  arrange(day) %>% 
  ggplot(aes(x=day, y=totaldailyappuse_avg)) +
  geom_line() + 
  labs(title = "Total App Usage per Day",
       y = "Total Usage (Average by Number of Users logged in each day)",
       x = "Day") +
  scale_x_continuous(  breaks = c(1:14,1)) +
    theme_classic()
# dat.appuse_long.ts <- ts(dat.appuse_long["totaldailyappuse"], start = 1, frequency = 1)
# str(dat.appuse_long.ts)
# autoplot(dat.appuse_long.ts) +
#   labs("Total App Usage per Day",
#        y = "Total App Usage",
#        x = "Day")
 
```
For each area, there's a downward trend of total app usage (sum of app usage, averaged by the number of users in each area) over the span of 14 days. Missing data in days 10-14 are not imputed here.
```{r}
dat.appuse.demo %>% 
  group_by(metro_area) %>%
  summarise_at(vars(day1:day14),
               funs(usersizeperday=sum(!is.na(.)), 
                    totalappuse=sum(., na.rm = TRUE))) %>%
  pivot_longer(cols = day1_usersizeperday:day14_totalappuse,
               names_to = c("usersize_perday_totalappuse"),
               values_to = c("value")) %>%
  separate(col = "usersize_perday_totalappuse", c("day","type"),sep = "_") %>%
  pivot_wider(names_from = c("type"),
             values_from = c("value")) %>%
  separate(col = "day", c("name","day"),"day") %>% select(-name) %>% 
  left_join(
  dat.appuse.demo %>% 
    group_by(metro_area) %>%
    summarise(user_size_by_region = n()) ,
  by=c("metro_area" = "metro_area")) %>%
  mutate(day = as.numeric(day),
         totaldailyappuse_avg=totalappuse/user_size_by_region 
         ,totaldailyappuse_avg_perday=totalappuse/usersizeperday
         ) -> dat.appuse.demo_usage_byregion
```

```{r}
dat.appuse.demo_usage_byregion %>%
  ggplot(aes(x=day, y=totaldailyappuse_avg_perday)) +
  geom_line() + 
  labs(title = "Total App Usage per Day for Each Metro Area",
       y = "Total Usage 
       (Averaged by Number of Users logged in each day)",
       x = "Day") +
    theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + 
  facet_wrap(~metro_area, nrow = 4)
```

```{r}
dat.appuse.demo_usage_byregion %>%
  ggplot(aes(x=day, y=totaldailyappuse_avg)) +
  geom_line() + 
  labs(title = "Total App Usage per Day for Each Metro Area",
       y = "Total Usage 
       (Average by the number of Users in that region)",
       x = "Day") +
    theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + 
  facet_wrap(~metro_area, nrow = 4) 
# dat.appuse_long.metro_area.ts <- ts(dat.appuse_long.metro_area["totaldailyappuse"], start = 1, frequency = 1)
# str(dat.appuse_long.metro_area.ts)
# 
# autoplot(dat.appuse_long.metro_area.ts, facets = TRUE) +
#   labs("Total App Usage per Day",
#        y = "Total App Usage",
#        x = "Day")
```
### explore trends in different demographics (metro_area, gender, age_range)
#### metro_area

```{r}
# https://stackoverflow.com/questions/30385415/r-map-plot-without-longitude-and-latitude 
# length(unique(dat.appuse.demo$userid)) # N = 3811
# nrow(dat.appuse.demo)
table(dat.appuse.demo$metro_area)

dat.appuse.demo %>% 
  group_by(metro_area) %>%
  summarise(user_size_by_region = n(),
            user_size_by_region_perc = round(user_size_by_region/3811*100,2)) %>% 
  arrange(desc(user_size_by_region_perc)) %>%
  # select(metro_area,user_size_by_region) %>%
  # arrange(desc(user_size_by_region)) %>%
  ggplot(aes(x=reorder(metro_area, -user_size_by_region_perc) ,y = user_size_by_region_perc)) +
  geom_bar(stat="identity") + 
  labs(title = "Total User Size by Metro Area",
      x = "Metro Area",
      y = "Total User Size (%)") +
  geom_text(aes(label = paste0(user_size_by_region_perc,"%")), hjust=1.2, color="white", size=3.5) +
  theme_classic() +
  coord_flip() 
```
There's not much difference in terms of total usage overtimee (averaged by the numbers of users) in different areas
```{r}
dat.appuse.demo %>% 
  group_by(metro_area) %>%
  summarise_at(vars(day1:day14),funs(sum(., na.rm = TRUE))) %>%
  mutate(totalusebyregion = 
           rowSums(.[,c(paste0("day",seq(1,14,1)))], na.rm = T)) %>%
  left_join(
    dat.appuse.demo %>% 
      group_by(metro_area) %>%
      summarise(user_size_by_region = n()),
    by=c("metro_area" = "metro_area")) %>%
  mutate(averageusebyregion = 
           round(totalusebyregion/user_size_by_region,digits = 2)) %>%
  ggplot(aes(x=reorder(metro_area, -averageusebyregion),y = averageusebyregion)) +
  geom_bar(stat="identity") + 
  labs(title = "Total App Usage by Metro Area",
      x = "Metro Area",
      y = "Total User Size (averaged by user size)") +
  geom_text(aes(label=averageusebyregion), hjust=1.2, color="white", size=3.5) +
  theme_classic() +
  coord_flip() 
```



#### gender
```{r}
table(dat.appuse.demo$gender)
dat.appuse.demo %>% 
  group_by(gender) %>%
  summarise(user_size_by_gender = n(),
            user_size_by_gender_perc = round(user_size_by_gender/3811*100,2)) %>% 
  # arrange(desc(user_size_by_gender)) %>%
  # select(gender,user_size_by_gender) %>%
  ggplot(aes(x=reorder(gender, -user_size_by_gender_perc) ,y = user_size_by_gender_perc)) +
  geom_bar(stat="identity") + 
  labs(title = "Total User Size by Gender",
      x = "Gender",
      y = "Total User Size (%)") +
  geom_text(aes(label = paste0(user_size_by_gender_perc,"%")), hjust=1.2, color="white", size=3.5) +
  theme_classic() +
    theme(axis.text.x = element_text(color = "grey20", size = 10, angle = 0, hjust = .5, vjust = .5, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 10, angle = 0, hjust = 1, vjust = 0, face = "plain"), 
        axis.title.x = element_text(color = "grey20", size = 12, angle = 0, hjust = .5, vjust = 0, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 12, angle = 90, hjust = .5, vjust = .5, face = "plain")) +   coord_flip() 
```

```{r}
dat.appuse.demo_gender_nonmissinguser <-dat.appuse.demo %>%
       group_by(gender) %>%
       summarise_at(vars(day1:day14),
               funs(usersizeperday=sum(!is.na(.)))) %>%
       pivot_longer(cols = day1_usersizeperday:day14_usersizeperday,
                    names_to = "day_usersizeperday",
                    values_to = "usersizeperday") %>%
       separate(day_usersizeperday, c("day","type"),sep="_") %>%
       separate(col = "day", c("name","day"),"day") %>%
       select(-type,-name)
dat.appuse.demo_gender_nonmissinguser
```
not much gender differences in terms of total usage (averaged by the number of users for each gender)
```{r}
dat.appuse.demo %>% 
  group_by(gender) %>%
  summarise_at(vars(day1:day14),funs(sum(., na.rm = TRUE))) %>%
  mutate(totalusebygender = 
           rowSums(.[,c(paste0("day",seq(1,14,1)))], na.rm = T)) %>%
  # pivot_longer(cols = day1:day14,
  #              names_to = "day",
  #              values_to = totalusebygender)
  left_join(
  dat.appuse.demo %>% 
  group_by(gender) %>%
  summarise(user_size_by_gender = n()) %>% 
  arrange(desc(user_size_by_gender)) %>%
  select(gender,user_size_by_gender)
  ,by = c("gender" = "gender")
  ) %>%
  select(gender, user_size_by_gender,totalusebygender) %>%
  mutate(totalusebygender_avg = totalusebygender/user_size_by_gender)

```

#### age_range

```{r}
table(dat.appuse.demo$age_range)

dat.appuse.demo %>% 
  group_by(age_range) %>%
  summarise(user_size_by_age = n(),
            user_size_by_age_perc = round(user_size_by_age/3811*100,2)) %>% 
  # arrange(desc(user_size_by_age)) %>%
  # select(gender,user_size_by_age) %>%
  ggplot(aes(x=reorder(age_range, -user_size_by_age_perc) ,y = user_size_by_age_perc)) +
  geom_bar(stat="identity") + 
  labs(title = "Total User Size by Age Range",
      x = "Age Range",
      y = "Total User Size (%)") +
  geom_text(aes(label = paste0(user_size_by_age_perc,"%")), hjust=1.2, color="white", size=3.5) +
  theme_classic() +
  coord_flip() 


dat.appuse.demo %>% 
  group_by(age_range) %>%
  summarise(user_size_by_age = n()) %>% 
  arrange(desc(user_size_by_age)) %>%
  select(age_range,user_size_by_age) %>%
  left_join(
    dat.appuse.demo %>% 
  group_by(age_range) %>%
  summarise_at(vars(day1:day14),funs(sum(., na.rm = TRUE))) %>%
  mutate(totalusebyage = 
           rowSums(.[,c(paste0("day",seq(1,14,1)))], na.rm = T))
  , by = c("age_range" = "age_range")
  ) %>% 
  mutate(totalusebyage_avg = totalusebyage/user_size_by_age) %>%
  arrange(desc(user_size_by_age)) %>%
  select(age_range,user_size_by_age, totalusebyage, totalusebyage_avg)
    
    
    

```

### User Experience Data
First, look at descriptive statistics

```{r}
glimpse(dat.userex)

dat.userex %>%
  group_by(time) %>%
  summarise_at(vars(-userid), funs(M = round(mean(., na.rm = T),2), 
                                   SD = round(sd(., na.rm = T),2))) %>%
  pivot_longer(cols = -time,
               names_to = "Item_Statistic",
               values_to = "value") %>%
  separate(col = Item_Statistic,
           c("Item","Statistic_Type"),
           sep = "_") %>%
  pivot_wider(names_from = "Statistic_Type", values_from = "value") %>%
  pivot_wider(names_from = "time",values_from = c("M","SD"))

```
Distribution of responses to each item: All overwhelmingly positive
```{r}
dat.userex %>% filter(time %in% "sign up") %>% select(3) %>% hist()
dat.userex %>% filter(time %in% "sign up") %>% select(4) %>% hist()
dat.userex %>% filter(time %in% "sign up") %>% select(5) %>% hist()
dat.userex %>% filter(time %in% "sign up") %>% select(6) %>% hist()
dat.userex %>% filter(time %in% "sign up") %>% select(7) %>% hist()
dat.userex %>% filter(time %in% "sign up") %>% select(8) %>% hist()

dat.userex %>% filter(time %in% "post-14 days")  %>% select(8) %>% hist()
dat.userex %>% filter(time %in% "post-14 days")  %>% select(9) %>% hist()


```
Correlations among items when signing up: items are highly correlated
```{r}
library(Hmisc)
library(stats)
rcorr(dat.userex %>% filter(time %in% "sign up") %>% select(3:8) %>% as.matrix(), type = "pearson")[[1]] %>% round(2)
```
Correlations between the two items post 14 days:
```{r}
rcorr(dat.userex %>% filter(time %in% "post-14 days") %>% select(8:9) %>% as.matrix(), type = "pearson")[[1]] %>% round(2)
```


```{r}
rcorr(dat.userex %>% filter(time %in% "sign up") %>% select(1,3) %>% 
        left_join(
      dat.userex %>% filter(time %in% "post-14 days") %>% select(1,9),
      by = c("userid" = "userid")) %>% select(-userid) %>%as.matrix(), 
      type = "pearson")[[1]] %>% round(2)
```


### missing data in usage data
In dat.appuse file: missing values are MCAR or MAR and need to be addressed accordingly.--> use multiple imputation
```{r}
# https://sebastiansauer.github.io/sum-isna/
# explore missing data in appuse data set
# check how many are missing
dat.appuse.demo %>% 
  summarise_at(vars(day1:day14), funs(sum(is.na(.))))
# days 11-14 have more missing values
apply(dat.appuse.demo %>% select(day1:day14), 1, function(x)sum(is.na(x))) %>% table()

apply(dat.appuse.demo %>% select(day1:day14), 1, function(x)sum(is.na(x))) %>% table()/3811
# 928(24.35%) users missed 4 days

# check if there's a consistent pattern between missing and other variables (e.g., region)
dat.appuse.demo %>% 
  group_by(metro_area) %>%
  summarise_at(vars(day1:day14), funs(sum(is.na(.))/n()))  %>%
  select(metro_area,day11:day14)
```

address missings using multiple imputations
```{r}
library(mice)
set.seed(55555)
dat.appuse.imp<- mice(dat.appuse.demo %>% select(day10:day14), m = 5)
dat.appuse.imp.complete <- complete(dat.appuse.imp)
glimpse(dat.appuse.imp.complete)
# sum(is.na(dat.appuse.imp.complete))

dat.appuse.demo.MIcompleted <- dat.appuse.demo %>%
  select(userid:day9, age_range,gender,metro_area) %>%
  bind_cols(dat.appuse.imp.complete) %>% 
  select(userid,day1:day9,day10:day14,everything()) %>%
  mutate(totalappuse = 
           rowSums(.[,c(paste0("day",seq(1,14,1)))], na.rm = T)) 
dat.appuse.demo.MIcompleted

# dat.appuse.demo.MIcompleted$totalappuse = rowSums(dat.appuse.demo.MIcompleted%>%select(day1:day14))
```

```{r}
dat.appuse.demo.MIcompleted %>% 
  summarise_at(vars(day1:day14),funs(sum(., na.rm = TRUE))) %>%
  pivot_longer(cols = day1:day14,
               names_to = "day",
               values_to = "totaldailyappuse") %>%
  separate(col = "day", c("name","day"),"day") %>% select(-name) %>% 
  mutate(day = as.numeric(day),
         totaldailyappuse_avg = totaldailyappuse/3811) %>%
  arrange(day) %>% 
  ggplot(aes(x=day, y=totaldailyappuse_avg)) +
  geom_line() + 
  labs(title = "Total App Usage per Day per User(imputed)",
       y = "Total App Usage",
       x = "Day") +
    scale_x_continuous(  breaks = c(1:14,1)) +
    theme_classic()

```

# Typology/Profiles of Users
#### LPA on users' responses immediately after signing up to examine the typology of users
```{r}
dat.userex %>% 
  group_by(time) %>%
  summarise_at(vars(-userid), funs(sum(!is.na(.)))) %>% t()

dat.userex_signup <- dat.userex %>% filter(time %in% "sign up") %>% select(1, 3:8)
glimpse(dat.userex_signup)
dat.userex_post14 <- dat.userex %>% filter(time %in% "post-14 days") %>% select(1, 8:9)
glimpse(dat.userex_post14)
```
Estimate Latent Profiles: Profile 4 has better model fit indices (lower AIC and BIC than Profile 3 and Profile 5, significant BLRT_p, more parsimonious than Profile 5)
```{r}
library(tidyLPA)
library(mclust)

dat.userex_signup %>% select("I expect this meditation app to be helpful.":"Recently I have felt stressed") -> dat.userex_signup_LPA
names(dat.userex_signup_LPA) <- paste0(rep("item",6), seq(1:6))

dat.userex_signup_LPA%>% 
  single_imputation() %>%
  estimate_profiles(n_profiles = 1:6,
                    models = 1) -> userex_signup_LPA
get_fit(userex_signup_LPA)

#Profile 4 has better model fit indices (lower AIC and BIC than Profile 3 and Profile 5, significant BLRT_p, more parsimonious than Profile 5)

dat.userex_signup_LPA %>% 
  single_imputation() %>%
  estimate_profiles(4, models = 1) -> dat.userex_signup_LPA_P4

dat.userex_signup_LPA_P4 %>%
  plot_profiles( rawdata = FALSE,add_line = TRUE)
```

```{r}
get_data(dat.userex_signup_LPA_P4) %>% select(item1:item6,Class) %>% 
  bind_cols(dat.userex_signup %>% select(userid)) -> dat.userex_signup_P4

dat.userex_signup_P4 %>% 
  group_by(Class) %>%
  summarise_at(vars(item1:item6), ~mean(., na.rm = T)) %>%
  pivot_longer(cols = item1:item6,
               names_to = "item",
               values_to = "rating") %>%
  separate(col = item, c("item","itemnumber"),"item") %>% select(-item) %>%
  mutate(itemnumber = as.numeric(itemnumber),
         Class = as.character(Class)) -> dat.userex_signup_P4_long
dat.userex_signup_P4_long

```

```{r}
dat.userex_signup_P4_long %>%
  rename(Profile = Class) %>%
  ggplot(aes(x = itemnumber, y = rating, col = Profile)) +
  geom_line() + 
  labs(title = "4 User Profiles",
       y = "Mean Response",
       x = "Item") +
  scale_x_continuous(  breaks = c(1:7,1)) +
  theme_classic()
```

```{r, echo=FALSE}

# dat.userex_signup_P4_long%>%
#   ggplot() + 
#   geom_line(data = dat.userex_signup_P4_long %>% filter(Class %in% "1"), 
#             aes(x = itemnumber, y = rating),color = "blue") + 
#     geom_line(data = dat.userex_signup_P4_long %>% filter(Class %in% "2"), 
#             aes(x = itemnumber, y = rating),color = "red") +
#     geom_line(data = dat.userex_signup_P4_long %>% filter(Class %in% "3"), 
#             aes(x = itemnumber, y = rating),color = "black")+
#     geom_line(data = dat.userex_signup_P4_long %>% filter(Class %in% "4"), 
#             aes(x = itemnumber, y = rating),color = "green")+
#   labs(title = "4 Profiles of Users",
#        y = "Mean Response",
#        x = "Item") + 
#   theme_classic()
``` 


# What are driving total app usage?

```{r}
# combine usage data, demo data, and sign-up survey data + class
dat.appuse.demo.MIcompleted.userex_signup_P4 <- dat.appuse.demo.MIcompleted %>%
  left_join(dat.userex_signup_P4,
            by = c("userid" = "userid")) %>%
  mutate(Class = as.character(Class),
         item_total = item1+item2+item3+item4+item5+item6) %>%
  filter_at(vars(starts_with("item")), any_vars(!is.na(.)))

glimpse(dat.appuse.demo.MIcompleted.userex_signup_P4)
# 
# dim(dat.userex_signup_P4)
```

there's a slight gender difference in total app use
```{r, echo=FALSE}
# # anova(lm(totalappuse~., data = dat.appuse.demo.MIcompleted.userex_signup_P4 %>%
# #              select(totalappuse, metro_area)))
# # anova(lm(totalappuse~., data = dat.appuse.demo.MIcompleted.userex_signup_P4 %>%
# #              select(totalappuse, age_range)))
# # #there's a gender difference
# # anova(lm(totalappuse~., data = dat.appuse.demo.MIcompleted.userex_signup_P4 %>%
# #              select(totalappuse, gender)))
# # anova(lm(totalappuse~., data = dat.appuse.demo.MIcompleted.userex_signup_P4 %>%
# #              select(totalappuse, gender,age_range)))
# anova(lm(totalappuse~., data = dat.appuse.demo.MIcompleted.userex_signup_P4 %>%
#              select(totalappuse
#                     ,gender
#                     ,age_range
#                     ,metro_area
#                     )))
# TukeyHSD(aov(lm(totalappuse~., data = dat.appuse.demo.MIcompleted.userex_signup_P4 %>%
#                   select(totalappuse
#                     ,gender
#                     ,age_range
#                     ,metro_area
#                     ))))
```
Age and Gender drives usage

```{r}
# summary(lm(totalappuse~., data = dat.appuse.demo.MIcompleted.userex_signup_P4 %>% 
             # select(totalappuse, gender,age_range,metro_area)))
summary(lm(totalappuse~., data = dat.appuse.demo.MIcompleted.userex_signup_P4 %>% 
             select(totalappuse, gender)))
summary(lm(totalappuse~., data = dat.appuse.demo.MIcompleted.userex_signup_P4 %>% 
             select(totalappuse,age_range)))
summary(lm(totalappuse~., data = dat.appuse.demo.MIcompleted.userex_signup_P4 %>% 
             select(totalappuse, metro_area)))
```

```{r}
dat.appuse.demo.MIcompleted.userex_signup_P4 %>% group_by(gender) %>%
  summarise_at(vars(totalappuse), funs(M = mean(., na.rm = T), 
                                 sd = sd(., na.rm = T),
                                 stderror = sd(., na.rm = T) / sqrt((length(.))))) %>%
  mutate_if(is.numeric, ~round(., digits = 2)) %>%
    ggplot(aes(x=gender,
             y = M
             )) + 
  geom_bar(stat="identity") +
  theme_classic() + 
    labs(title = "Gender Differences in Total App Usage",
      x = "Gender",
      y = "Mean Total Usage") +
  geom_text(aes(label = paste0(M)), hjust=1.2, color="white", size=3.5) +
    theme(axis.text.x = element_text(color = "grey20", size = 10, angle = 0, hjust = .5, vjust = .5, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 10, angle = 45, hjust = 1, vjust = 0, face = "plain"), 
        axis.title.x = element_text(color = "grey20", size = 12, angle = 0, hjust = .5, vjust = 0, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 12, angle = 90, hjust = .5, vjust = .5, face = "plain")) +   coord_flip()

```

```{r}

dat.appuse.demo.MIcompleted.userex_signup_P4 %>% group_by(age_range) %>%
  summarise_at(vars(totalappuse), funs(M = mean(., na.rm = T), 
                                 sd = sd(., na.rm = T),
                                 stderror = sd(., na.rm = T) / sqrt((length(.))))) %>%
  mutate_if(is.numeric, ~round(., digits = 2)) %>%
    ggplot(aes(x=age_range,
             y = M
             )) + 
  geom_bar(stat="identity") +
  theme_classic() + 
    labs(title = "Age Differences in Total App Usage",
      x = "Age Range",
      y = "Mean Total Usage") +
  geom_text(aes(label = paste0(M)), hjust=1.2, color="white", size=3.5) +
    theme(axis.text.x = element_text(color = "grey20", size = 10, angle = 0, hjust = .5, vjust = .5, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 10, angle = 45, hjust = 1, vjust = 0, face = "plain"), 
        axis.title.x = element_text(color = "grey20", size = 12, angle = 0, hjust = .5, vjust = 0, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 12, angle = 90, hjust = .5, vjust = .5, face = "plain")) +  coord_flip()

```

Users' latent profiles ~ total usage
```{r}
summary(lm(totalappuse~., data = dat.appuse.demo.MIcompleted.userex_signup_P4 %>% 
             select(totalappuse, Class)))
```
sign-up items ~ totalappuse
```{r}
source("Correlation_matrix_function.R")
correlations <- cormatrix(dat.appuse.demo.MIcompleted.userex_signup_P4 %>% dplyr::select(totalappuse, item1:item6)) 
rownames(correlations) = names(correlations)
correlations
```


```{r}
summary(lm(totalappuse~., data = dat.appuse.demo.MIcompleted.userex_signup_P4 %>% 
             select(totalappuse, item1:item6)))
```
sign-up user survey total score does not predict total usage
```{r}
summary(lm(totalappuse~., data = dat.appuse.demo.MIcompleted.userex_signup_P4 %>% 
             select(totalappuse, item_total)))
```


```{r}
library(rwa)
dat.appuse.demo.MIcompleted.userex_signup_P4 %>%
  rwa(outcome = "totalappuse",
      predictors = c(paste0(rep("item",6),seq(1:6))),
      applysigns = TRUE) -> dat.out.rwa.userex

dat.out.rwa.userex$"result" %>% 
  mutate_if(is.numeric,~round(., 2)) %>%
  ggplot(aes(x=Variables,
             #reorder(Variables, -Sign.Rescaled.RelWeight),
             # y = Sign.Rescaled.RelWeight
             y = Rescaled.RelWeight
             )) + 
  geom_bar(stat="identity") +
  theme_classic() + 
    labs(title = "Relative Contribution of Survey Items (after sign up) to Total Usage",
      x = "Item",
      y = "Relative Contribution to Total Usage (%)") +
  geom_text(aes(label = paste0(Rescaled.RelWeight)), hjust=-0.1, color="black", size=2.8) +
    theme(axis.text.x = element_text(color = "grey20", size = 10, angle = 0, hjust = .5, vjust = .5, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 10, angle = 0, hjust = 1, vjust = 0, face = "plain"), 
        axis.title.x = element_text(color = "grey20", size = 12, angle = 0, hjust = .5, vjust = 0, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 12, angle = 90, hjust = .5, vjust = .5, face = "plain")) +   coord_flip()

```


### what predicts change in stress level
```{r}
# library(lme4)
library(nlme)
dat.userex.recode <- dat.userex %>% mutate(
  time_code = case_when(
    time %in% "sign up" ~ "1",
    time %in% "post-14 days" ~ "2"
  ),
  time_code = as.numeric(time_code)
) #%>%
  # mutate(time_code = as.factor(time_code),
  #        time = as.factor(time),
  #        userid = as.factor(userid))

names(dat.userex.recode) <- c("userid","time",paste0(rep("item",7),seq(1:7)),"time_code")

glimpse(dat.userex.recode)

dat.appuse.demo.MIcompleted.userex_signup_P4.long <- dat.userex.recode %>% 
  left_join(
  dat.appuse.demo.MIcompleted.userex_signup_P4 %>% select(userid:totalappuse, Class,item1:item5),
  by = c("userid" = "userid")
)  %>%
  mutate(total_item1thru5_signup = item1.y + item2.y + item3.y + item4.y + item5.y)
glimpse(dat.appuse.demo.MIcompleted.userex_signup_P4.long)
```

whether there's an increase/decrease in stress level between sign-up and 14 days later: There's a significant decrease in the level of stress after using the app for 14 days
```{r}
dat.appuse.demo.MIcompleted.userex_signup_P4.long %>% group_by(time) %>% summarise_at(vars(item6),funs(mean(., rm.na = T)))

# sum(is.na(dat.userex_stress_prepost))
HLM_model_stress_prepost <- lme(fixed = item6~time_code, 
                                random = ~1|userid,
                                # random = ~time_code|userid, #time as random slope
                            data = dat.appuse.demo.MIcompleted.userex_signup_P4.long) 
summary(HLM_model_stress_prepost)
```

# What predicts decreased level of stress right after signing up and 14 days later?
User profiles and Time, certain metro areas predict change in the levels of stress
```{r}


# Items 1,2,4 predict change
HLM_model_stress_prepost_predictors <- lme(fixed =
                                             item6 ~ time_code + totalappuse
                                           + Class
                                           # + item1.y + item2.y + item3.y + item4.y + item5.y
                                           + total_item1thru5_signup
                                           + age_range 
                                           + gender 
                                           + metro_area
                                           , random = ~1|userid,
                                #time as random slope
                            data = dat.appuse.demo.MIcompleted.userex_signup_P4.long)
summary(HLM_model_stress_prepost_predictors)
# view(dat.appuse.demo.MIcompleted.userex_signup_P4.long)

# anova(HLM_model_stress_prepost,HLM_model_stress_prepost_predictors)
```
```{r}
dat.appuse.demo.MIcompleted.userex_signup_P4.long %>% group_by(time_code,Class) %>%
  summarise_at(vars(item6), funs(M = mean(., na.rm = T), 
                                 sd = sd(., na.rm = T),
                                 stderror = sd(., na.rm = T) / sqrt((length(.))))) %>% 
  mutate(Profile = as.character(Class)) %>%
  ggplot(aes(x = time_code, y = M)) +
  geom_line() + 
  labs(title = "Change in Stress From Sign-up to post-14 days",
       y = "Mean Stress Level",
       x = "Time Point") + 
  scale_x_continuous( breaks = c(1:2,1)) +
  # scale_x_discrete( breaks = c("0","1"), labels = c("sign up","14 days later")) +
  facet_wrap(~Profile) +
    theme_bw() + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
  

```

